True versus apparent shapes of astrophysical bow shocks

### 2016-06-14 papers/Paper1/sec-conclusions.tex
New start on Jorge's paper
Start writting conclusions

\section{Application to proplyd bowshocks}
\label{sec:application}

>>>>

\section{Conclusions}
\label{sec:conc}

\newcommand\thC{\(\theta^1\)\,Ori~C}
\defcitealias{Canto:1996}{CRW}

We developed a method to estimate the shape of a generic bow shock product of the
interaction of two winds and was applies to the proplyds in the core of the ONC.
We started measuring the projected characteristic radii $(R'_0,R'_c)$ for each proplyd in our
sample and compare them with the ``conic equivalent'' of a two winds interaction model based 
on \CRW{} work to estimate the intrinsic bow shock shape and get the stagnation pressure.
Most results are consistent with a proplyd's photoevaporated flow with an anisotropic density
distribution, with different anisotropy degrees. We ound that LV4 has the least anisotropic flow,
while LV2 has the most anisotropic flow.
